### 2021-09-06 manuscript/field_data.tex
Valores de média e std nos dados reais corrigidos

We set the equivalent layer at $300$ meters above the ground.
By applying our method to the interpolated regular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data 
(Figure \ref{fig:carajas_gz_predito_mag_gridline}a) and its data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_gridline}b), with mean of $0.07979$ nT and the standart deviation of $0.5060$ nT  revealing an acceptable data fitting.
Our method converges at about 200 iterations,  taking $390.80$ seconds with a Intel core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes.

By applying our method to the decimated iregular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we  obtain the  predicted data 
(Figure \ref{fig:carajas_gz_predito_mag_decimated}a) and its data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_decimated}b), with mean of  of $0.07348$ nT and standart deviation of $0.3172$ nT. This application took $385.56$ seconds to complete the estimative.
Figure \ref{fig:convergence_carajas_mag_decimated} shows the convergence curve, up to $2,000$ iterations, revealing a good convergence rate by applying our method to the decimated irregular grid. 
This result shows the  robustness of our method in processing irregular grid.

>>>>

We set the equivalent layer at $300$ meters above the ground.
By applying our method to the interpolated regular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data 
(Figure \ref{fig:carajas_gz_predito_mag_gridline}a) and its data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_gridline}b), with mean of $0.0762$ nT and the standart deviation of $0.4886$ nT  revealing an acceptable data fitting.
Our method converges at about 200 iterations,  taking $390.80$ seconds with a Intel core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes.

By applying our method to the decimated iregular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we  obtain the  predicted data 
(Figure \ref{fig:carajas_gz_predito_mag_decimated}a) and its data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_decimated}b), with mean of  of $0.0717$ nT and standart deviation of $0.3144$ nT. This application took $385.56$ seconds to complete the estimative.
Figure \ref{fig:convergence_carajas_mag_decimated} shows the convergence curve, up to $2,000$ iterations, revealing a good convergence rate by applying our method to the decimated irregular grid. 
This result shows the  robustness of our method in processing irregular grid.
